Maximum likelihood estimation of cardinalities\\ from HyperLogLog sketches

### 2016-05-03 paper/paper.tex
added a paragraph to the result section

\autoref{fig:estimation_error_12_14}

>>>>

We also evaluated the case $\symPrecision = 12$ and $\symRegRange=14$, which is interesting, because the register values are limited to the range $[0, 15]$. As a consequence, 4 bits are sufficient for representing a single register value. This allows two registers to share a single byte, which is beneficial from a performance perspective. Nevertheless, this configuration still allows the estimation of cardinalities up to 100 millions as shown in \autoref{fig:estimation_error_12_14}, which could be enough for many applications.
